---
title: "Crated Parallel Map Functions"
output: html_document
date: "2025-06-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(purrr)
mirai::daemons(6)
```

The following code errors:
```{r, error=TRUE}

slow_lm <- function(formula, data) {
  Sys.sleep(1)
  lm(formula, data = data)
}

models <- mtcars |>
  split(mtcars$cyl) |>
  map(\(df) slow_lm(mpg ~ disp, data = df), .parallel = TRUE)

```


Possible solutions:

(1) Require manual crating of the anonymous function using:

```{r}
models <- mtcars |>
  split(mtcars$cyl) |>
  map(carrier::crate(\(df) slow_lm(mpg ~ disp, data = df), slow_lm = slow_lm), .parallel = TRUE)
```

(2) Use the `.parallel` argument to pass a list:
```{r}
models <- mtcars |>
  split(mtcars$cyl) |>
  map(\(df) slow_lm(mpg ~ disp, data = df), .parallel = list(slow_lm = slow_lm))
```

(3) Simplify slightly by allowing a vector of object names:
```{r}
models <- mtcars |>
  split(mtcars$cyl) |>
  map(\(df) slow_lm(mpg ~ disp, data = df), .parallel = c("slow_lm"))
```

(4) Use a parallel scope whereby everything inside gets crated and also turns on parallel mapping:
```{r, eval=FALSE}
models <- parallel({
  slow_lm <- slow_lm

  mtcars |>
    split(mtcars$cyl) |>
    map(\(df) slow_lm(mpg ~ disp, data = df))
})
```

Other considered solutions:

1. Using the `...` argument of `purrr::map()`, which currently errors if used in the parallel case. However this creates a divergence in use vs. the non-parallel case - i.e. if the parallel case below (top) were to work, then the non-parallel case (bottom) would error.

```{r, eval=FALSE}
# add slow_lm to the auto crate env
models <- mtcars |>
  split(mtcars$cyl) |>
  map(\(df) slow_lm(mpg ~ disp, data = df), slow_lm = slow_lm, .parallel = TRUE)

# pass slow_lm as an argument to the lambda (which would error)
models <- mtcars |>
  split(mtcars$cyl) |>
  map(\(df) slow_lm(mpg ~ disp, data = df), slow_lm = slow_lm)
```

2. Create a special case which automagically works for a single argument function to a single function call. However, it could make it confusing / difficult to reason with the code, if this then fails for an anonymous function for a more complex function call such as:

```{r, eval=FALSE}
models <- mtcars |>
  split(mtcars$cyl) |>
  map(\(df) {
    x <- slow_lm(mpg ~ disp, data = df)
    y <- slow_lm(mpg ~ disp, data = df)
    list(x, y)
  })
```
